---
title: "Overview of aws.alexa"
author: "Gaurav Sood"
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Overview of aws.alexa}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### Client for the Alexa Web Information Services API

Find information about domains, including the kind of content that they carry, how popular are they, sites linking to them, among other things.

The package provides access to the [Alexa Web Information Service API](http://docs.aws.amazon.com/AlexaWebInfoService/). 

### Installation

To get the current development version from github:

```{r, eval=FALSE, install}
# install.packages("devtools")
devtools::install_github("cloudyr/aws.alexa", build_vignettes = TRUE)
```

### Usage

To get going, get the application id and password from [https://console.aws.amazon.com/iam/home#security_credential](https://console.aws.amazon.com/iam/home#security_credential). Then set the application id and password via the `set_secret_key` function.

```{r, eval=FALSE, setapp}
set_secret_key(key="key", secret="secret")
```

#### 