---
title: "Overview of aws.alexa"
author: "Gaurav Sood"
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Overview of aws.alexa}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### Client for the Alexa Web Information Services API

Find information about domains, including the kind of content that they carry, how popular are they, sites linking to them, among other things.

The package provides access to the [Alexa Web Information Service API](http://docs.aws.amazon.com/AlexaWebInfoService/latest/). 

### Installation

To get the current development version from github:

```{r, eval=FALSE, install}
# install.packages("devtools")
devtools::install_github("cloudyr/aws.alexa", build_vignettes = TRUE)
```

### Usage

To get going, get the application id and password from [https://aws.amazon.com/](https://aws.amazon.com/). Then set the application id and password via the `set_secret_key` function.

```{r, eval=FALSE, setapp}
set_secret_key(key="key", secret="secret")
```

#### URL Information 

```{r, eval=FALSE, url_info}
res <- url_info("http://www.google.com")
res <- do.call(cbind, lapply(res[[2]][[1]][[2]], as.data.frame))
dimnames(res) <- list(1:nrow(res),  c("url", "attribute", "title", "description", "online_since"))
return(res)
```

```
##          url attribute  title
## 1 google.com/ canonical Google
                                                                                                                            description
## 1 Enables users to search the world's information, including webpages, images, and videos. Offers unique features and search technology.
##  online_since
## 1  15-Sep-1997
```
#### Traffic History 

```{r, eval=FALSE, traffic_hist}
traffic <- traffic_history("http://www.google.com")
head(traffic)
```

```
##         Date PageViews.PerMillion PageViews.PerUser Rank Reach.PerMillion
## 1 2016-04-22               105330             16.18    1           436000
## 2 2016-04-23                78490             12.30    2           414000
## 3 2016-04-24                75310             11.94    2           413600
## 4 2016-04-25               112420             17.90    1           436800
## 5 2016-04-26               114280             17.79    1           447300
## 6 2016-04-27               111610             17.41    1           440200
```

#### Browse Categories 

```{r, eval=FALSE, browse_cats}
browse_categories(path="Top/Arts")
```

#### Category Listings

```{r, eval=FALSE, cat_list}
cat_list <- category_listing(path="Top/Arts")
head(cat_list)
```

```
##                                   DataUrl.text DataUrl..attrs                       Title PopularityRank AverageReview
## 1                      http://www.youtube.com/      navigable                     YouTube              2       4.12195
## 2 http://www.facebook.com/#!/JeffDunham?ref=ts      navigable                    Facebook              4             4
## 3            http://twitter.com/#!/nbctheevent      navigable          Twitter: The Event             13             4
## 4                         http://www.imdb.com/      navigable The Internet Movie Database             65           4.5
## 5                          http://www.cnn.com/      navigable                         CNN             98           2.5
## 6                        http://www.bbc.co.uk/      navigable                  BBC Online            107             4
##                                                                                              Description
## 1                                             User-submitted videos with rating, comments, and contests.
## 2 A social utility that connects people, to keep up with friends, upload photos, share links and videos.
## 3                                               Official Twitter account for the series, at @nbcthevent.
## 4                                   Features plot summaries, reviews, cast lists, and theatre schedules.
## 5                                                                                     Cable News Network
## 6                                                          The BBC Homepage - Your gateway to BBC Online

```

#### In Links

```{r, eval=FALSE, in_links}
res_links <- in_links(url="google.com")
head(res_links)
```

```
##         Title                                                                                                                                 Url
## 1 youtube.com     m.youtube.com:80/?client=mv-google&p=1&nomobile=1&desktop_uri=/?gl=KE&p=1&client=mv-google&hl=fil&nomobile=1&hl=fil&app=m&gl=KE
## 2  amazon.com                                                                                                                 alexa.amazon.com:80
## 3   yahoo.com                 ar.news.qa1p.global.media.yahoo.com:80/blogs/ciencia-bruja/mario-bunge-y-el-detector-fama-cient-fica-171403253.html
## 4    ebay.com community.ebay.com:80/t5/Archive-International-Trading/Can-not-pay-One-or-more-of-the-items-below-cannot-be-purchased/qaq-p/4981427
## 5 yahoo.co.jp                                                                            blog.olp.yahoo.co.jp:80/archives/20130128_mapupdate.html
## 6   baidu.com                                                                                       anquan.baidu.com:80/bbs/thread-86224-1-1.html
```